Modelling the emergence of whisker barrels

### 2020-07-13 paper/briefpaper/brief.tex
Update to the We reasoned... sentence

\mpfive{We reasoned that an arbitrary number of distinct field locations may
  be determined by a minimum of two guidance fields, if a tendency for the
  density of projections to concentrate is appropriately balanced with
  the tendency of projections that interact more strongly with the guidance
  fields to migrate further in the directions specified by their
  gradients. Accordingly, projections that interact most strongly with a given
  guidance gradient would come to occupy cortical locations at which that
  field has extreme values, leaving adjacent locations available to be
  occupied by projections with the next strongest interactions, and so
  forth. This would in principle allow the \emph{relative} locations of the
  fields to be specified by the relative values of the interaction parameters,
  $\gamma$, and hence for a topological map in the cortex to be specified by a
  spatial ordering of the $\gamma$ values at the level of the thalamus.}

>>>>

\mpfive{We reasoned that an arbitrary number of distinct field locations may
  be determined by a minimum of two guidance gradients, if the concentration
  of the projection densities is influenced by competition between
  projections, and if a projection that interacts more strongly with a given
  guidance gradient migrates further in the direction of that gradient.
  Accordingly, projections that interact most strongly with a given
  guidance gradient would come to occupy cortical locations at which that
  field has extreme values, leaving adjacent locations available to be
  occupied by projections with the next strongest interactions, and so
  forth. This would in principle allow the \emph{relative} locations of the
  fields to be specified by the relative values of the interaction parameters,
  $\gamma$, and hence for a topological map in the cortex to be specified by a
  spatial ordering of the $\gamma$ values at the level of the thalamus.}
